### 2020-07-01 abstract.tex
intro

\begin{abstract}
\label{abstract}
We use smartphones everywhere and privacy concerns have arisen for the ``shoulder surfing'' attack, where strangers peek at our phone in public areas. To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) technique, a malicious attacker can peek from farther away with the assist of his/her smartphone camera and SR algorithms, rendering the underestimated threat model. To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) architecture for multi-image SR. We implement SPPeek in Android. The experimental results demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses. And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.
\end{abstract}

>>>>

\begin{abstract}
\label{abstract}
We use smartphones everywhere and privacy concerns have arisen for the ``shoulder surfing'' attack, where strangers peek at our phone in public areas. To mitigate this privacy threat, various countermeasures have been designed but mainly against attackers with the naked eye. With the development of smartphones and super resolution (SR) techniques, a malicious attacker can peek from further away with the assist of the smartphone camera and SR algorithms, rendering the underestimated shoulder surfing threat model. To underline this concern, we present SRPeek, an end-to-end system of shoulder surfing deployed on commercial smartphones, including a unique deep neural network (DNN) for multi-image SR. We implement SPPeek in Android and conduct comprehensive experiments in controlled and real life scenarios. Evaluations demonstrate its efficiency and robustness, allowing a human to read 90\% of the characters at a distance of 1.8m with traditional lenses and 6m with optical zooming lenses. And it outperforms the state-of-the-arts and fills the blank space of multi-image SR for shoulder surfing attack.
\end{abstract}

### 2020-07-01 introduction.tex
intro

The privacy threat however has been exacerbated with the rapidly developed mobile camera module these years. Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones. Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second. And more images mean more recorded information of the victim. Given the commercial smartphone, the attacker can record the information reliably for propagating. For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}. To gain vital data more stealthily and accurately from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be further employed by the attacker, delivering a long-range shoulder surfing threat model.

@@

Unfortunately, none of existing work can mitigate the new threat model. Specifically, massive efforts have been made, from physical privacy films to alternative password entry interfaces \cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods \cite{kumar2007reducing}. All of these methods however require additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios. Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios. Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it is imminent to recall attention on this new privacy threat and propose the corresponding countermeasure for modern circumstances.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{pic/illustration.pdf}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm.}
	\label{illustration_of_system}
\end{figure}

\vspace{1mm}
\noindent
\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{illustration_of_system}. 
While the victim's reading private information in public, the attacker, standing within 1.8 meters behind him, raises his commercial smartphone, zooms in on the victim's screen, takes 10 to 20 snapshots rapidly in burst mode(about 10 frames per second), and process them with a multi-frame SR system to generate a high-res result. The whole process takes only a few seconds and can even be repeated at a 2 second interval to give the attacker a continuous surveillance over the victim's screen, not missing any detail, while at the same time, few people would suspect a stranger holding his smartphone at 1.8 meters behind them. With the newest generation of smartphones equipped with telephoto lenses and capable of optical zooming, this distance can be raised to a staggering 6 meters, posing a silent but deadly threat to screen privacy.

@@

% \begin{figure}
% 	\centering
% 	\includegraphics[width=0.48\textwidth]{pic/zeros.png}
%     \caption{Photos of number ‘0’ on a screen at a distance of 1.5m, taken in quick succession from a still smartphone camera. All exhibit different blurriness and no consistency between neighboring frames.\cl{Figure should be replaced.}}
% 	\label{illustration_of_system}
% \end{figure}

@@

  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing. It can be further exacerbated by straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts, requiring a reliable ``reconstruction'' than ``interpolation''. Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character. 
  % In deep learning based methods, a deep network often leads to gradual divergence from the truth as the data is propagated deeper through the network pipeline, resulting in 'fake' high-res images, especially when the subjects are the discrete strokes of characters, instead of details and texture of everyday objects. As a matter of fact, most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two. 
  On one hand, each snapshot is blurred with a randomly different PSF kernel, removing the consistency between neighboring frames, shown in Figure~\ref{illustration_of_system}. Thus it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle, posing a greater demand for interigation abilities of the SR algorithms than most other SR applications.

@@

  \item \textbf{Super resolution with multiple frames.} To resolve the blurriness of input images, a SR algorithm on a smartphone is required to recover the captured contents. However, none of existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred snapshots as input. Since smartphones can capture 10 snapshots per second in burst mode. Specifically, the difference between videos and multiple snapshots rules out existing image/video super resolution algorithms\cite{lucas2019generative} \cite{kappeler2016video}. The reason has two folds. First, either increased input leads to increases in model complexity, making it unsuitable for mobile deployment. Second, the nature of our task requires to do pixel-wise correlation and comparison with same coordinates on consecutive images throughout our construction process. Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this snapshot.
  \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on commercial smartphones in a real-time manner rather than remotely in cloud server. Since 1) the latter would require stable Internet access, and 2) sending multiple images across the Internet will consume time and bandwidth. Given the required 10 to 20 images to process for ideal content recovery, we have 1-2s as the minimum interval between each output frame, rendering limited period for calculation with restricted power and RAM. In cases where the display on the target screen changes more frequently, less images and processing time are available for each scene. Consequently, it cannot only require a smaller and simpler network model, but also a model that can deal with dynamic inputs efficiently, either 3 or 20 images.
  \item \textbf{Complexities of characters.} To deploy our threat model broadly for real-life scenarios (e.g., record passwords or e-mails), it is supposed to reconstruct multi-type texts, including Chinese characters, English letters, and numbers. Composed of multiple strokes, characters are distributed discretely in the pixel-wise image and different with other entities (e.g., faces and natural objects), rendering unique challenges. In some cases, messing up a stroke even slightly can shorten or lengthen a stroke, leading to a different character for misunderstandings. Unlike most SR applications working on similarity between their output and the ground truth, our network architecture and training process must be engineered to recover readable contents. Another challenge is the imbalanced element for words. Since we know certain stroke or alphabet of Chinese and English characters can occur more frequently, results in lower prediction accuracy over the less common, unconventionality shaped characters.

@@

\vspace{1mm}
\noindent
\textbf{Summary of Evaluation Results.}
Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's phone with above 90\% accuracy at 2m distance on a smartphone without optical zooming, or 6m distance on a phone with optical zooming in our experimental settings. The system is able to capture snapshots and produce high-res images constantly with about 2 seconds interval. Our experiments with real life scenarios show that this system is able to decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a threat to screen privacy.

\vspace{1mm}
\noindent
\textbf{Contributions.} This paper makes the following contributions:
\begin{itemize}[leftmargin=*]
  \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
  \item	We design a multi-frame SR neural network architecture aiming at reconstructing extremely massive blurred and defocused snapshots. It can be further extended to other text-recognition applications on commercial smartphones.
  \item	We evaluate this new shoulder surfing attack in comprehensive scenarios. And it outperforms the state-of-the-arts for the new privacy concern.
\end{itemize}
% describe the organization of the paper

>>>>

The privacy concerns however have been exacerbated with the rapidly developed mobile camera module these years. Equipped with multiple cameras, the newest generation of smartphones can perform 100$\times$ zooming compared to the standard 5$\times$ of single camera phones. Hardware improvements in memory also allows the burst mode at tremendous frame rates and even high-speed photography, delivering videos with thousands of frames per second. Given the commercial smartphone, the attacker can record the information reliably for propagating. And more images mean more recorded information of the victim. For example, in a Senate hearing, the Justice Secretary of Philippines, Vitaliano Aguirre II, suffered a leakage of his text messages, as someone had taken a snapshot of his smartphone \cite{Polotiko2017leakage}. To gain vital data more stealthily and accurately from even further away, the processing technique of multi-frame super resolution (SR) algorithms can be further employed by the attacker, delivering a long-range shoulder surfing threat model.

@@

Unfortunately, none of existing work can mitigate this new threat model. Specifically, massive efforts have been made, from physical privacy films to alternative password entry interfaces~\cite{wiedenbeck2006design,papadopoulos2017illusionpin} and input methods~\cite{kumar2007reducing}. All of these methods however require the additional deployment cost \cite{Chun2019Keep} and cannot be widely deployed for critical privacy stages (e.g., password entry) of most scenarios. Furthermore, none of existing works can deal with the presence of developed smartphone cameras and SR algorithms in shoulder surfing scenarios. Given the ubiquitous usages of smartphones and serious damages of the data disclosure for the victim, it is imminent to recall attention on this new threat model and propose corresponding countermeasure for modern circumstances.

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{pic/illustration.pdf}
    \caption{Illustration of the long-range shoulder surfing threat model on smartphones, exacerbated by the SR algorithm.}
	\label{illustration_of_system}
\end{figure}

\vspace{1mm}
\noindent
\textbf{Threat Model.} We present \textsf{SRPeek}, an end-to-end system of shoulder surfing using the SR algorithm, illustrated in Figure~\ref{illustration_of_system}. 
While the victim's reading private information in public, the attacker, standing within 1.8 meters behind him, raises his commercial smartphone and zooms in on the victim's screen. Then he can take 10 to 20 snapshots rapidly in burst mode (about 10 frames per second), and process them with a multi-frame SR technique to generate a high-resolution result. The whole process only takes a few seconds and can even be repeated at a 2 second interval, enabling the attacker to monitor the victim's screen continuously, not missing any detail. Meanwhile, few people would suspect a stranger holding his smartphone at 1.8 meters behind them. Given the newest generation of smartphones equipped with telephoto lenses and capable of optical zooming, this distance can reach a staggering 6 meters, posing a silent but deadly threat to screen privacy.

@@

@@

  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing. It can be further exacerbated by straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts as Figure~\ref{illustration_of_system} shows, requiring a reliable ``reconstruction'' than ``interpolation''. Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character. 
  % In deep learning based methods, a deep network often leads to gradual divergence from the truth as the data is propagated deeper through the network pipeline, resulting in 'fake' high-resolution images, especially when the subjects are the discrete strokes of characters, instead of details and texture of everyday objects. As a matter of fact, most works on multi-frame SR function on video clips \cite{lucas2019generative} or multiple snapshots \cite{wronski2019handheld}, however, our application is subtly different from the two. 
  On one hand, each snapshot is blurred with a randomly different PSF kernel, removing the consistency between neighboring frames. Thus it cannot be approximated as video clips using a constant, isotropic gaussian kernel; on the other hand, each defocused snapshot only contains fractions of information, analogous to pieces of a jigsaw puzzle. Thus it poses a greater demand for integration abilities of the SR algorithms than most other SR applications.

@@

  \item \textbf{Super resolution with multiple snapshots.} To resolve the blurriness of input snapshots, a SR algorithm on a smartphone is required to recover the blurred contents. However, none of existing SR algorithms can be adapted for this attack scenario, especially with massive extremely blurred snapshots as input. Since smartphones can capture 10 snapshots per second in burst mode. Specifically, the difference between videos and multiple snapshots rules out existing image/video super resolution algorithms~\cite{lucas2019generative,kappeler2016video}. The reason has two folds. First, massive input leads to the increase in model complexity, making it unsuitable for mobile deployment. Second, the nature of our task requires to do pixel-wise correlation and comparison in the same coordinate with consecutive snapshots throughout our construction process. Otherwise we cannot tell if, for example, it is one stroke or two parallel strokes that is shown in these two darker pixels on this snapshot.
  \item \textbf{Model complexity and variable input.} We have to operate our threat model locally on commercial smartphones in a real-time manner rather than remotely in cloud server. Since 1) the latter requires a stable internet access, and 2) sending multiple snapshots across the Internet will consume time and bandwidth. Given the required 10 to 20 snapshots to be processed for the ideal content recovery, we have 1-2 seconds as the minimum interval between each output frame, rendering a limited period for calculation with the restricted power and RAM. In case where the display on the target screen changes more frequently, fewer snapshots and less processing time are available for each scene. Consequently, it cannot only require a more precise network model, but also a model that can deal with dynamic inputs efficiently, either 3 or 20 snapshots.
  \item \textbf{Complexities of characters.} To deploy our threat model broadly for real-life scenarios (e.g., record passwords or e-mails), it is supposed to reconstruct complex characters with multiple strokes, such as Chinese characters shown in Figure~\ref{illustration_of_system}. Composed of multiple strokes, characters are distributed discretely in the pixel-wise snapshot and different with other entities (e.g., faces and natural objects), rendering unique challenges. In some cases, messing up a stroke even slightly can shorten or lengthen a stroke, leading to a different character for misunderstandings. Unlike most SR applications working on similarity between their output and the ground truth, our network architecture and training process must be engineered to recover readable contents. Another challenge is the imbalanced element for words. Since we know certain stroke or alphabet of Chinese and English characters can occur more frequently, results in lower prediction accuracy over the less common, unconventionality shaped characters.

@@

\vspace{1mm}
\noindent
\textbf{Summary of Evaluation Results.}
Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's screen with above 90\% accuracy at 1.8m distance on a smartphone without optical zooming, or 6m on a phone with optical zooming in our experimental settings. \textsf{SRPeek} can capture snapshots and produce high-resolution images constantly with about 2 seconds interval. Our experiments in real life scenarios show that it can decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a serious threat to screen privacy.

\vspace{1mm}
\noindent
\textbf{Contributions.} This paper makes the following contributions:
\begin{itemize}[leftmargin=*]
  \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range, which can be deployed on commercial smartphones. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
  \item	We design a multi-frame SR neural network architecture to reconstruct massive extremely blurred and defocused snapshots. It can be further extended to other text-recognition applications.
  \item	We evaluate this new shoulder surfing threat model in multiple scenarios. And it outperforms the state-of-the-arts for the new privacy concern.
\end{itemize}
% describe the organization of the paper
